### 2018-03-10 paper/implementations.tex
Add a few more comments

>>>>

\todo{NM}{To me \hs{M} is a bit mysterious. Maybe show its internals?}

\todo{NM}{What about using shorter \hs{get} and \hs{put}? I can introduce it right in the common vocabulary, mentioning the usual get-put laws. I would also remove `get' prefixes from many functions, e.g. \hs{dependencies compute} reads fine. This is a minor issue, happy to do this at the end.}

\todo{NM}{The API still uses \hs{Map k v} and it looks this needs updating throughout the section, so I'll stop here.}
